%------------------------
% Author : Bhuvi Vishwakarma
% Based off of: https://github.com/16bhuvi/Resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% colors
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ 
      \textit{#3} & {\color{dark-grey} \small #4}\\ 
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Bhuvi Vishwakarma} \\ \vspace{5pt}
    \small \faPhone* \texttt{+91 8176851701} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{bhuvi162005@email.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faGithub \hspace{2pt} \texttt{github.com/16bhuvi} \hspace{1pt}
    
    \hspace{1pt} \faLinkedin \hspace{2pt} \texttt{linkedin.com/in/bhuvi-vishwakarma} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{India}
    \\ \vspace{-3pt}
\end{center}

%-----------SUMMARY-----------
\section{PROFESSIONAL SUMMARY}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     {Final-year IT Engineering student focused on \textbf{Software Engineering, Data Analysis, and Prompt Engineering}. Determined to apply technical foundations alongside interests in \textbf{Finance, HR, Economic and Creative Design}.} \vspace{2pt} \\
     {Proactive collaborator experienced in managing projects from development to final \textbf{presentation and social engagement}.} \vspace{2pt} \\
     {Seeking to leverage strong \textbf{communication skills} to contribute to high-value projects and multidisciplinary team goals.}
    }}
 \end{itemize}
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

\resumeSubheading
      {Findem}{May 2025 -- June 2025}
      {Software Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Python-based web scraper} to automate the extraction of leadership metrics from corporate websites; open-sourced the development repository on {\href{https://github.com/16bhuvi/Web_Scrapping}{\myuline {GitHub}}}.}
        \resumeItem{Acquired proficiency in industry-standard development workflows under senior mentorship, worked and engaged in their live projects as a part of Software engineer team including \textbf{Git version control}, systematic debugging, and \textbf{API fetching}.}
        \resumeItem{Leveraged \textbf{Postman} for API testing and \textbf{MongoDB Compass} for managing and visualizing scraped JSON data structures.}
        \resumeItem{Conducted \textbf{data research and analysis} on internal web architecture to identify functional gaps and improve data processing efficiency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{ACE Your Day}}{Mar. 2025 -- Apr. 2025}
      \resumeItemListStart
        \resumeItem{Developed an all-in-one student management application using \textbf{Object-Oriented Programming (OOP) in C++} to centralize personal tasks, course schedules, and meal planning.}
        \resumeItem{Engineered a comprehensive organizational suite featuring dynamic to-do lists and academic tracking to streamline daily routines for students.}
        \resumeItem{Integrated an interactive \textbf{mini-game component} to increase user engagement and balance productivity with user experience.}
        \resumeItem{Open-sourced the project repository and technical documentation on {\href{https://github.com/16bhuvi/ACE-Your-Day-Student-Scheduler-}{\myuline {GitHub}}}.}
      \resumeItemListEnd
          
        \resumeProjectHeading
      {\textbf{Leadership Data Scraper}}{May 2025 -- June 2025}
      \resumeItemListStart
        \resumeItem{Engineered a \textbf{Python-based web scraper} to automate the extraction of organizational leadership data from various corporate websites.}
        \resumeItem{Utilized \textbf{Postman} for API testing and \textbf{MongoDB Compass} for managing and visualizing scraped \textbf{JSON} data structures, ensuring high data accuracy.}
        \resumeItem{Performed in-depth \textbf{data research and analysis} on web architectures to optimize scraping logic and handle dynamic content delivery.}
        \resumeItem{Implemented industry-standard workflows including \textbf{Git version control} and systematic debugging for efficient codebase maintenance.}
        \resumeItem{Published the development repository and technical implementation details on {\href{https://github.com/16bhuvi/Web_Scrapping}{\myuline {GitHub}}}.}
      \resumeItemListEnd
          
      \resumeProjectHeading
      {\textbf{Amazon Clone - BookStore}}{Feb. 2025}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive static clone of the Amazon e-commerce platform, specifically tailored for a book-shopping experience using \textbf{semantic HTML}.}
        \resumeItem{Architected a multi-page interface including landing pages, product catalogs, and shopping cart layouts to demonstrate mastery of web document structure and linking.}
        \resumeItem{Implemented complex layouts and navigation menus, focusing on replicating a well-known production-level UI for an \textbf{Internet Web Technologies} academic assignment.}
        \resumeItem{Deployed the live static site on \textbf{Netlify} for optimized delivery and accessible project demonstration: {\href{https://amazon-bv.netlify.app/}{\myuline {amazon-bv.netlify.app}}}.}
      \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{BanVerse | AI-Powered Student Platform}}{Aug. 2025 -- Mar. 2026}
        \resumeItemListStart
          \resumeItem{Co-developed a comprehensive student engagement ecosystem featuring an \textbf{AI-driven chatbot} for automated grievance handling and \textbf{intelligent recommendation algorithms} for campus events.}
          \resumeItem{Spearheaded the \textbf{UI/UX design}, creating a highly user-friendly and responsive interface to facilitate seamless interaction for the university student body.}
          \resumeItem{Managed the end-to-end \textbf{deployment cycle}, including a complex 10-hour configuration of a \textbf{custom virtual machine} environment within the university network infrastructure.}
          \resumeItem{Optimized platform accessibility by deploying a live production build on \textbf{Netlify}: {\href{https://banverse-01.netlify.app/}{\myuline {banverse-01.netlify.app}}}.}
          \resumeItem{Collaborated in an agile team environment over a 3-month development sprint, open-sourced on {\href{https://github.com/16bhuvi/Ban-Verse}{\myuline {GitHub}}}.}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd

\section{ACHIEVEMENTS \& PARTICIPATIONS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{AlgoUniversity Tech Fellowship (ATF 2024)}: Successfully qualified Stage-1, standing out among the \textbf{top 20\%} of 20,000+ applicants and advancing to Stage-2 within the \textbf{top 4\%} of candidates.\vspace{2pt} \\
     \textbf{Google Cloud Skills Boost Arcade}: Reached the \textbf{Arcade Novice Tier} (Season 1, 2025) by completing 100+ hands-on labs and achieving multiple milestones in cloud infrastructure and services.\vspace{2pt} \\
     \textbf{30-Hour Hackverse (AIC Banasthali)}: Collaborated in a team to develop \textbf{"Reuse \& Earn"}, a full-stack sustainable trading platform using Python, MySQL, and Web Technologies; successfully cleared two evaluation rounds.\vspace{2pt} \\
     \textbf{BV-Literati Face Painting Competition}: Secured \textbf{Second Place} at the annual academic fest of the Department of English \& Modern European Languages, themed around "Indian Literature and Culture." \vspace{2pt} \\
     \textbf{MAYUKH 2025}: Actively participated in the Technical Festival at Banasthali Vidyapith, contributing as an \textbf{Anchor} and coordinating filler segments for cultural event block.\vspace{2pt} \\
     \textbf{Project Navonmesh}: Recognized for volunteer contributions during the "Igniting The Spark Within" initiative led by the Global Institute for Circular Economy and Sustainable Development Goals.\vspace{2pt} \\
     \textbf{In-House Project:} Our project \textbf{BanVerse} ranked among the top 30 out of approximately 141 projects during the session 2025--26 B.Tech. (CS/IT/CS-AI) in our university.
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Banasthali Vidyapith}{July 2023 -- Present}
      {Bachelor of Technology in Information Technology}{Tonk, Rajasthan}
      \resumeItemListStart
        \resumeItem{\textbf{CGPA}: 7.8 / 10.0 (Cumulative of 5 Semesters)}
        \resumeItem{\textbf{Relevant Coursework}: Data Structures and Algorithms, Database, Internet Web Technologies, Object-Oriented Programming, Operating Systems, Software Engineering, Engineering economics, Management, Basic Engineering architecture \& core, Entrepreneurship.}
      \resumeItemListEnd

    \resumeSubheading
      {Ryan International School}{Completed 2021 -- 2023}
      {Secondary \& Senior Secondary (CBSE)}{Shahjahanpur, Uttar Pradesh}
      \resumeItemListStart
        \resumeItem{\textbf{Class XII (2023)}: 75\% in PCM, Computer Science, and English.}
        \resumeItem{\textbf{Class X (2021)}: 94\% Aggregate.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C, C++, Java, SQL (MySQL)}\vspace{2pt} \\
     \textbf{Web Technologies}{: HTML, CSS, JavaScript, JSON, React.js, MongoDB}\vspace{2pt} \\
     \textbf{Core Fundamentals}{: OOP, DSA, DBMS, OS, Prompt Engineering, Project management and presentation}\vspace{2pt} \\
     \textbf{Tools \& Software}{: Git, GitHub, Postman, AutoCAD, Virtual Machine (Virtual Box), Canva}\vspace{2pt} \\
     \textbf{Additional Skills}{: Drone Technology, Web Scraping}
    }}
 \end{itemize}
\end{document}
